Human tissue specific markers

### 2017-06-08 manuscript/manuscript.Rnw
re-enable grid.text

legend("bottomright",       legend=paste0(capwords(a)," ",c("1 Read","10 Reads","1000 Reads", "5000 Reads")),
       col=c("brown","green","#002058", "#E87722"),
       lwd=2)
}
### grid.text(c("A","B","C","D"),
###           x=unit(c(0,0.5,0,0.5),"npc"),
###           y=unit(c(1,1,0.5,0.5),"npc"),
###           just=c("left","top"),
###           gp=gpar(fontsize=32)
###           )

@@

\caption{\ac{ROC} curve of the placenta \ac{SVM} (A) and
  uterus \ac{SVM} (B) . Both \ac{SVM} are highly effective at
  distinguishing between samples of uterus origin and non-uterus
  origin.
  %
  \ac{ROC} curve of reduced reads in Placenta and
  Uterus samples with the indicated number of total reads. Reads were
  reduced by sampling reads for each sample weighted by the FPKM
  measured for each sample, and run using the same trained SVM
  depicted in Figure \ref{fig:plac_ut_full_roc}. %
  % 
  The placenta \ac{SVM} is fairly accurate at distinguishing between
  samples of placental origin and non-placental origin even when the
  number of reads is very low (10). The uterus \ac{SVM} requires many
  more reads in order to achieve similar accuracy. This is likely due
  to the much smaller number of uterus specific genes in comparison to
  placenta.}
\label{fig:plac_ut_roc}
\end{figure}

>>>>

legend("bottomright",       legend=paste0(capwords(a)," ",c("1 Read","10 Reads","1000 Reads", "5000 Reads")),
       col=c("brown","green","#002058", "#E87722"),
       lwd=2)
}
grid.text(c("A","B","C","D"),
          x=unit(c(0,0.5,0,0.5),"npc"),
          y=unit(c(1,1,0.5,0.5),"npc"),
          just=c("left","top"),
          gp=gpar(fontsize=32)
          )

@@

\caption{\ac{ROC} curve of the placenta \ac{SVM} (A,C) and
  uterus \ac{SVM} (B,D) . Both \ac{SVM} are highly effective at
  distinguishing between samples of uterus origin and non-uterus
  origin using the entirety of reads from a sample.
  %
  \ac{ROC} curve of reduced reads in Placenta (C) and
  Uterus (D) samples with the indicated number of total reads. Reads were
  reduced by sampling reads for each sample weighted by the FPKM
  measured for each sample, and run using the same trained SVM
  from the full runs.
  % 
  The placenta \ac{SVM} is fairly accurate at distinguishing between
  samples of placental origin and non-placental origin even when the
  number of reads is very low (10). The uterus \ac{SVM} requires many
  more reads in order to achieve similar accuracy. This is likely due
  to the much smaller number of uterus specific genes in comparison to
  placenta.}
\label{fig:plac_ut_roc}
\end{figure}
